AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-03-03 article/tex/main.tex
polishes section air4children

That said, in a first phase, AIR4Children project will be piloting teaching materials with our open source robots and Otto, a well known open source educational robot \cite{OttoDIY:2016}.  
Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops to be free of charge to all the participants. 
In this regard, this initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate children's perception on the fields of AI and Robotics.

@@

\subsection{Open teaching materials}
Considering teaching materials of AI and Robotics to be child-like oriented, AIR4Children is then adopting Montessori's education with philosophy orbited around the quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) and computational thinking (e.g. variables, loops, counters, etc) \cite{bers2012, resnick1998}.
Similarly, as Elkin et al. (2014) \cite{elkin2014} explained, AIR4Children can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
  \caption{(a) Spiral learning divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
  %\Description{.}
  \label{fig:tm}
\end{figure}

>>>>

In a first phase, AIR4Children project will be piloting teaching materials with our open source robots and Otto, a well known open source educational robot \cite{OttoDIY:2016}.  
Then in a second phase, and with feedback of the pilots, teaching materials with child-centre programing languages as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops to be free of charge to all the participants. 
In this regard, this initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate children's perception on the fields of AI and Robotics.

@@

\subsection{Open teaching materials}
Considering teaching materials of AI and Robotics to be child-like oriented, AIR4Children is then adopting Montessori's education with the philosophy orbited around the quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for AIR4Children are based on Montessori education to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) and computational thinking (e.g. variables, loops, counters, etc) \cite{bers2012, resnick1998}.
Similarly, as Elkin et al. (2014) \cite{elkin2014} explained, AIR4Children can provide a way to engage children in problem-solving activities to allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}, fig \ref{fig:tm}(b) shows material of otto robot to develop creative exploration and engage in collaborative activitities and fig \ref{fig:tm}(c) a block diagram as a child-centre programing language.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
  \caption{(a) Spiral learning divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
  %\Description{.}
  \label{fig:tm}
\end{figure}
